Hurricane Evacuation Strategies for the State of Mississippi

### 2015-11-16 manuscript.tex
added code

\section{Stochastic Model of Landfall-Avodiant Evacuations}
\label{sec:stochastic}
  \subsection{Model Description}
    \par In this model, instead of giving citizens particular evacuation plan, we give them a simple rule: move directly away from the hurricane landfall if possible, else move North or North-West. Using the statewide broadcast system, the state of Mississippi can tell its citizens where the expected landfall will be, and which counties will be the most affected. In which case, individual citizens are instructed to leave the counties that will be flooded, and to do so as outlined above. This means less coordination from the state, and more options for each citizens. At the cost of not having designated areas, and therefore designated refuge areas for citizens, evacuation is faster because it involves less per-county organization.\\
    \par As opposed to the model described in \nameref{sec:maxflow}, we also allow citizens to leave the state of Mississippi. For example, Arkansas is less likely to be hit by the full force of hurricanes that move through Mississippi \cite{5news}, as such, it is a good place to take refuge while the storm passes. In order to achieve this, we add ``unofficial'' nodes in the graph representation of Mississippi. Figure~\ref{fig:highway_map} shows that Hancock and Jackson Counties have roads that lead into Louisiana and Alabama respectively, both of which are potential routes away from the Hurricane's landfall, meaning that such nodes are important when movement can also be lateral. Because we are only interested in the movement of citizens within Mississippi, we can assume that citizens that reach the out-of-state nodes keep moving further and further away from the hurricane, though we are not tracking them. We created four out-of-state nodes North, South, East and West of Mississippi, each connected in a way that satisfies the highways mapped in Figure~\ref{fig:highway_map}.
  \subsection{Parameter Values and Justification}
    \par The parameters to this model are the same as the parameters for the models outlined above, except that this model uses the complete highway map of Mississippi, instead of only considering vertical highways. This algorithm expects three inputs outside of the parameters: the first, less accurate estimate of the affected counties, the more accurate second estimate and the final, most accurate estimate. Notice that as described, these inputs actually abstract away the hurricane's category. Instead, the category is reflected by the
  \subsection{Results}
    \begin{figure}
      \center
      \begin{subfigure}[b]{0.5\textwidth}
        \center
        \includegraphics[width=\linewidth]{figures/pred_hancock-crop.pdf}
        \caption{Predicted Evacuation for Landfall in Hancock County}
      \end{subfigure}~
      \begin{subfigure}[b]{0.5\textwidth}
        \center
        \includegraphics[width=\linewidth]{figures/pred_jackson-crop.pdf}
        \caption{Predicted Evacuation for Landfall in Jackson County}
      \end{subfigure}
      \caption{}
    \end{figure}
  \subsection{Strengths and Weaknesses}

@@

>>>>

\section{Stochastic Model of Landfall-Avodiant Evacuations}
\label{sec:stochastic}
  \subsection{Model Description}
    \par In this model, instead of giving citizens particular evacuation plan, we give them a simple rule: move directly away from the hurricane landfall if possible, else move North or North-West. Using the statewide broadcast system, the state of Mississippi can tell its citizens where the expected landfall will be, and which counties will be the most affected. In which case, individual citizens are instructed to leave the counties that will be flooded, and to do so as outlined above. This means less coordination from the state, and more options for each citizens. At the cost of not having designated areas, and therefore designated refuge areas for citizens, evacuation is faster because it involves less per-county organization.\\
    \par As opposed to the model described in \nameref{sec:maxflow}, we also allow citizens to leave the state of Mississippi. For example, Arkansas is less likely to be hit by the full force of hurricanes that move through Mississippi \cite{5news}, as such, it is a good place to take refuge while the storm passes. In order to achieve this, we add ``unofficial'' nodes in the graph representation of Mississippi. Figure~\ref{fig:highway_map} shows that Hancock and Jackson Counties have roads that lead into Louisiana and Alabama respectively, both of which are potential routes away from the Hurricane's landfall, meaning that such nodes are important when movement can also be lateral. Because we are only interested in the movement of citizens within Mississippi, we can assume that citizens that reach the out-of-state nodes keep moving further and further away from the hurricane, though we are not tracking them. We created four out-of-state nodes North, South, East and West of Mississippi, each connected in a way that satisfies the highways mapped in Figure~\ref{fig:highway_map}.
  \subsection{Parameter Values and Justification}
    \par The parameters to this model are the same as the parameters for the models outlined above, except that this model uses the complete highway map of Mississippi, instead of only considering vertical highways. This algorithm expects three inputs outside of the parameters: the first, less accurate estimate of the affected counties, the more accurate second estimate and the final, most accurate estimate. Notice that as described, these inputs actually abstract away the hurricane's category. Instead, the category is reflected by the size of the list of the affected counties given as the respective inputs for the estimates.
  \subsection{Results}
    \begin{figure}
      \center
      \begin{subfigure}[b]{0.5\textwidth}
        \center
        \includegraphics[width=\linewidth]{figures/pred_hancock-crop.pdf}
        \caption{Predicted Evacuation for Landfall in Hancock County}
      \end{subfigure}~
      \begin{subfigure}[b]{0.5\textwidth}
        \center
        \includegraphics[width=\linewidth]{figures/pred_jackson-crop.pdf}
        \caption{Predicted Evacuation for Landfall in Jackson County}
      \end{subfigure}
      \caption{}
    \end{figure}
  \subsection{Strengths and Weaknesses}

@@

\lstinputlisting[style=Matlab]{deterministic/certainties.m}
\lstinputlisting[style=Matlab]{deterministic/constantrate.m}
\lstinputlisting[style=Matlab]{deterministic/getA.m}
\lstinputlisting[style=Matlab]{deterministic/populations.m}
\lstinputlisting[style=Matlab]{deterministic/thresholds.m}
\lstinputlisting[style=Matlab]{hurricane_generator/interpolate_radius.m}
\lstinputlisting[style=Python]{deterministic/threshold.py}
\lstinputlisting[style=Python]{get_pop.py}
\lstinputlisting[style=Python]{stochastic/data.py}
\lstinputlisting[style=Python]{stochastic/simulation.py}
\lstinputlisting[style=Python]{stochastic/wolfram.py}
\lstinputlisting[style=Python]{get_adjacency.py}
\lstinputlisting[style=Python]{utils.py}
\lstinputlisting[style=Python]{hurricane_generator/clean.py}
\lstinputlisting[style=Python]{hurricane_generator/get_radii.py}
\lstinputlisting[style=Python]{hurricane_generator/geotag.py}
\lstinputlisting[style=Python]{hurricane_generator/final.py}
\lstinputlisting[style=Python]{flow/colornodes.py}
\lstinputlisting[style=Python]{flow/maxflow.py}
\lstinputlisting[style=Python]{flow/create_graph.py}
\lstinputlisting[style=Python]{flow/threshold_from_hurricane.py}
